Budgeted Reinforcement Learning\\in Continuous State Space

### 2019-11-24 paper/talk/edouard/main.tex
Update BMDP definition
Update examples and baseline

Examples?

\begin{frame}{Constrained Reinforcement Learning}
\begin{block}{\only<2>{Constrained} Markov Decision Process}
	A\only<1>{n} \alert<2>{\only<2>{C}MDP} is a tuple $(\cS, \cA, P, \Rr, \only<2>{\alert<2>{R_c,}} \gamma \only<2>{\alert{, \beta}})$ with:
	\begin{multicols}{2}
			\begin{itemize}
			\item Rewards $\Rr\in\Real^{\cS \times \cA}$
			\item[]
			\item<2> \alert<2>{Costs $R_c\in\Real^{\cS \times \cA}$}
			\item<2> \alert{Budget $\beta$}
		\end{itemize}
	\end{multicols}
\end{block}
\begin{block}{Objective}
Find $\pi^*$ such that $\forall s\in\cS$:
	\begin{equation*}
	\begin{array}{lcr}
	\displaystyle \pi^* \in \argmax_{\pi\in\cM(\cA)^{\cS}} \expectedvalue\left[\sum_{t=0}^\infty \gamma^t \Rr(s_t, a_t) \condbar s_0=s \right]\\
	\visible<2>{
	\text{ s.t. }  \displaystyle \alert<2>{\expectedvalue\left[\sum_{t=0}^\infty \gamma^t R_c(s_t, a_t) \condbar s_0=s\right] \leq \beta}}
	\end{array}
	\end{equation*}
\end{block}
\end{frame}

\begin{frame}{Budgeted Reinforcement Learning}
\begin{block}{Budgeted Markov Decision Process}
	A \alert{BMDP} is a tuple $(\cS, \cA, P, \Rr, \Rc, \gamma\alert{, \cB})$ with:
	\begin{multicols}{2}
		\begin{itemize}
			\item Rewards $\Rr\in\Real^{\cS \times \cA}$
			\item[]
			\item Costs $\Rc\in\Real^{\cS \times \cA}$
			\item \alert{Budget space $\cB$}
		\end{itemize}
	\end{multicols}
\end{block}
\begin{block}{Objective}
	Find $\pi^*$ such that $\forall\alert{(s,\beta)\in\cS\times\cB}$:
	\begin{equation*}
	\begin{array}{lcr}
	\displaystyle \pi^* \in \argmax_{\pi\in\cM(\cA \alert{\times \cB})^{\cS\alert{\times \cB}}} \expectedvalue\left[\sum_{t=0}^\infty \gamma^t R_r(s_t, a_t) \condbar s_0=s, \alert{\beta_0 = \beta}\right]\\
		\text{ s.t. }  \displaystyle \expectedvalue\left[\sum_{t=0}^\infty \gamma^t \Rc(s_t, a_t) \condbar s_0=s, \alert{\beta_0 = \beta}\right] \leq \beta
	\end{array}
	\end{equation*}
\end{block}
\end{frame}

@@

\begin{frame}{Performances}
\begin{itemize}
	\item Baseline: $\lambda$-FTQ, Lagrangian relaxation
	\begin{itemize}
		\item $R_r(s,a) \leftarrow R_r(s,a) - \lambda R_c(s,a) \text{ where } \lambda \geq 0$
	\end{itemize}.
\end{itemize}
\end{frame}

@@

\begin{center}
\includegraphics[trim={0 0cm 0 0.8cm}, clip, width=0.5\textwidth]{../../source/img/highway.pdf}\\
\href{https://budgeted-rl.github.io/\#driving-styles}{\includegraphics[width=0.5\linewidth]{img/highway_env}}
\end{center}

>>>>

Examples?
\end{frame}

\begin{frame}{Examples}
\begin{alertblock}{Dialogue systems}
A slot-filling problem: the agent fills a form by asking the user each slot. It can either:
\begin{itemize}
	\item ask to answer using {\green voice} {\green (safe/slow)};
	\item ask to answer with a {\red numeric pad} {\red (unsafe/fast)}.
\end{itemize}
\end{alertblock}

\begin{alertblock}{Autonomous Driving}
The agent is driving on a two-way road with a car in front of it,
\begin{itemize}
\item it can {\green stay behind} {\green (safe/slow)};
\item it can {\red overtake} {\red (unsafe/fast)}.
\end{itemize}
\begin{center}
\href{https://budgeted-rl.github.io/assets/highway-neutral.gif}{\includegraphics[width=0.5\linewidth]{img/highway_env}}
\end{center}
\end{alertblock}
\end{frame}

\begin{frame}{Constrained Reinforcement Learning}
\begin{alertblock}{\only<2>{Constrained} Markov Decision Process}
	A\only<1>{n} \alert<2>{\only<2>{C}MDP} is a tuple $(\cS, \cA, P, \Rr, \only<2>{\alert<2>{R_c,}} \gamma \only<2>{\alert{, \beta}})$ with:
	\begin{multicols}{2}
			\begin{itemize}
			\item Rewards $\Rr\in\Real^{\cS \times \cA}$
			\item[]
			\item<2> \alert<2>{Costs $R_c\in\Real^{\cS \times \cA}$}
			\item<2> \alert{Budget $\beta$}
		\end{itemize}
	\end{multicols}
\end{alertblock}
\begin{block}{Objective}
Maximise rewards \only<2>{\alert{while keeping costs under a fixed budget}}
	\begin{equation*}
	\begin{array}{rl}
	 \max_{\pi\in\cM(\cA)^{\cS}} &\expectedvalue\left[\sum_{t=0}^\infty \gamma^t \Rr(s_t, a_t) \condbar s_0=s \right]\\
	\visible<2>{
	\text{ s.t. }  \displaystyle &\alert<2>{\expectedvalue\left[\sum_{t=0}^\infty \gamma^t R_c(s_t, a_t) \condbar s_0=s\right] \leq \beta}}
	\end{array}
	\end{equation*}
\end{block}
\end{frame}

\begin{frame}{Budgeted Reinforcement Learning}
\begin{alertblock}{Budgeted Markov Decision Process}
	A \alert{BMDP} is a tuple $(\cS, \cA, P, \Rr, \Rc, \gamma\alert{, \cB})$ with:
	\begin{multicols}{2}
		\begin{itemize}
			\item Rewards $\Rr\in\Real^{\cS \times \cA}$
			\item[]
			\item Costs $\Rc\in\Real^{\cS \times \cA}$
			\item \alert{Budget space $\cB$}
		\end{itemize}
	\end{multicols}
\end{alertblock}
\begin{block}{Objective}
Maximise rewards while keeping costs under an \alert{adjustable} budget. $\alert{\forall \beta\in\cB},$
	\begin{align*}
	\begin{array}{rl}
	 \max_{\pi\in\cM(\cA \alert{\times \cB})^{\cS\alert{\times \cB}}} &\expectedvalue\left[\sum_{t=0}^\infty \gamma^t \Rr(s_t, a_t) \condbar s_0=s, \alert{\beta_0 = \beta}\right]\\
		\text{ s.t. } &\expectedvalue\left[\sum_{t=0}^\infty \gamma^t \Rc(s_t, a_t) \condbar s_0=s, \alert{\beta_0 = \beta}\right] \leq \beta
	\end{array}
	\end{align*}
\end{block}
\end{frame}

@@

\begin{frame}{A baseline approximate solution}
\begin{alertblock}{Lagrangian Relaxation}
	Consider the dual problem so as to replace the hard constraint by a soft constraint penalised by a \alert{Lagrangian  multiplier $\lambda$}:
	\begin{equation*}
	\label{eq:lagrangian-relaxation}
	\max_\pi \expectedvalue \sum_t {\green \gamma^t R_r(s,a)} - \alert{\lambda}{\red \gamma^t R_c(s,a)}
	\end{equation*}
	\begin{itemize}
		\item Train many policies $\pi_k$ with penalties $\lambda_k$ and recover the cost budgets $\beta_k$% (Theorem 4.4, \cite{Beutler85})
		\item Very data/memory-heavy
	\end{itemize}
\end{alertblock}
\end{frame}

@@

\begin{center}
\includegraphics[trim={0 0cm 0 0.8cm}, clip, width=0.5\textwidth]{../../source/img/highway.pdf}\\
\href{https://budgeted-rl.github.io/\#driving-styles}{\includegraphics[width=0.5\linewidth]{img/highway_env}}
\end{center}
\end{frame}
